RJObject Paper

### 2014-06-10 Documents/Paper/ms.tex
Sampling distribution
Sinewave data figure

>>>>

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point.

The simulated data is shown in Figure~\ref{fig:sinewave_data}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example.
\label{fig:sinewave_data}}
\end{center}
\end{figure}
